### 2019-02-23 soc.tex
replace BibTeX with BibLaTeX
This is a more convenient way to do citations, thanks to the biblatex-iso690 package (https://github.com/michal-h21/biblatex-iso690).
wrap bibliography figure numbers in square brackets

\usepackage[numbib, nottoc]{tocbibind}          % number bib, no TOC in TOC

@@

@@

% MISCELLANEOUS %
%-=============-%
\usepackage{amsmath, amstext}                   % math

\usepackage[font=small, labelfont=bf, figurename=Obr., tablename=Tab.]{caption}

\usepackage{enumitem}                           % lists

@@

  % create the bibliography
  \renewcommand{\refname}{Použitá literatura}
  \bibliographystyle{czechiso}
  \bibliography{soc}

>>>>

\usepackage[nottoc]{tocbibind}                  % no TOC in TOC

@@

% BIBLIOGRAPHY %
%-============-%
\usepackage[backend=biber,
            style=iso-numeric,
            sortlocale=cs_CZ,
            autolang=other,
            bibencoding=UTF8]{biblatex}         % use BibLaTeX for references
\addbibresource{soc.bib}                        % reference file

\renewcommand*{\finentrypunct}{}                % don't end the reference with .

\renewcommand{\multinamedelim}{\addcomma\space} % use comma as delimeter
\renewcommand{\finalnamedelim}{\addspace a \space} % use a as final name delim
\renewbibmacro{in:}{}                           % don't use In:

\DeclareFieldFormat{labelnumberwidth}{[#1]}     % wrap references in square br.

@@

% MISCELLANEOUS %
%-=============-%
\usepackage{amsmath, amstext}                   % math
\usepackage[font=small, labelfont=bf, figurename=Obr., tablename=Tab.]{caption}
\usepackage{enumitem}                           % lists

@@

  % create the bibliography
  \renewcommand{\refname}{Použitá literatura}
  \printbibliography[heading=bibnumbered]
